### 2024-02-05 README.Rmd
improvements to readme
add logo

@@

-   Secondly, just because two areas are separated by, say, a body of water, this does not mean that they are necessarily independent.

>>>>

# sfislands <img src="man/figures/logo.png" align="right" height="120" alt="" />

@@

-   Secondly, just because two areas are separated by, say, a body of water, this does not necessarily mean that they are to be considered independent of each other.
